Stateful Forward Reasoning

### 2025-01-31 paper.tex
Fix author info
Fix Unicode setup
Use hyperref; remove some comments

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
\usepackage{xcolor}
\usepackage{minted}
\usepackage{amsmath,amssymb}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
\usepackage{pgfplots}

@@

\newcommand{\xcom}[1]{{\color{cyan}{Xavier: #1}} }
\newcommand{\jcom}[1]{{\color{orange}{Jannis: #1}} }
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}
%
\begin{document}
%
\title{Stateful Forward Reasoning}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Munich (LMU), Munich, Germany\\
\email{\{xavier.genereux,jannis.limpberg\}@lmu.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{Forward Reasoning \and Proof Automation \and Theorem Proving.}
\end{abstract}
%
%
%

>>>>

\documentclass[runningheads]{llncs}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[british]{babel}
\usepackage{newunicodechar}
\usepackage{xcolor}
\usepackage{minted}
\usepackage{amsmath,amssymb}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{hyperref}

\renewcommand\UrlFont{\color{blue}\rmfamily}
\urlstyle{rm}

\newunicodechar{≔}{\ensuremath{\coloneq}}

@@

\newcommand{\xcom}[1]{{\color{cyan}{Xavier: #1}} }
\newcommand{\jcom}[1]{{\color{orange}{Jannis: #1}} }

\begin{document}

\title{Stateful Forward Reasoning}

%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here

\author{Jannis Limperg\inst{1}\orcidID{0000-0002-8861-5231} \and
  Xavier Généreux\inst{1}\orcidID{TODO}}

\authorrunning{J.~Limperg and X.~Généreux}
\institute{University of Munich (LMU), Munich, Germany\\
\email{\{xavier.genereux,jannis.limperg\}@lmu.de}}

\maketitle

\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{Forward Reasoning \and Proof Automation \and Theorem Proving.}
\end{abstract}
